---
Title: "FedRAMP High Baseline Controls Analysis"
---
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Install and load the following packages##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
```{r, results='hide'}
#install.packages("readxl")
#install.packages("readr")
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("igraph")
#install.packages("dplyr")
#install.packages("sqldf")
#install.packages("sna")
#install.packages("intergraph")
#install.packages("RColorBrewer")
#install.packages("randomcoloR")
#install.packages("caret")
#install.packages("reshape2")
```

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(readr)
#library(tidyverse)
```

```{r, results='hide'}
library(igraph)
library(sna)
library(intergraph)
library(RColorBrewer)
library(randomcoloR)
library(dplyr)
library(ggplot2)
library(caret) 
library(ggplot2) 
library(reshape2) 
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Data Cleaning##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##800-53 subcontrol relations
```{r}
#File path
Controls <- read_excel("/Users/eugenehwang/Documents/GitHub/FedRAMP_800-53_Controls/800-53 subcontrol relations.xlsx")

#Set working directory path
#setwd("/Users/eugenehwang/Documents/FedRAMP/Data")
setwd("/Users/eugenehwang/Documents/GitHub/FedRAMP_800-53_Controls")

#Get working directory path
getwd()

#Selecting only the columns needed and renaming columns with underscore **
Controls_mod <- Controls

names(Controls_mod) <- c("Control_Family","Family_Name","Control_Name", "Main_Control","Control_Enhancement_Name", "Control_Enhancement","Combined","Related_Controls","Low","Low_1","Tailoring_Action","Medium","Medium_1","High","High_1","Priority","Impact")

#Only looking at High Impact Controls
Gephi_Controls <- Controls_mod %>%
  filter(High == "Y") %>% #filtering to High Baseline
  select(Control_Family, Family_Name, Main_Control, Control_Name, Control_Enhancement, Combined, Related_Controls)
         #,Low, Medium, High, Impact, Tailoring_Action) 
```

##Spreading Related Controls into different columns.
**Gephi_Controls1**
```{r warning = FALSE}
Gephi_Controls1 <- Gephi_Controls %>%
  select(-Control_Enhancement) %>%
  separate(Related_Controls, paste("Related_Control", 1:28, sep = "_"),
           sep = ",", 
           extra = "warn") %>% #spreading Related Controls into different columns 
  mutate(Related_Control_1 = str_trim(Related_Control_1, side = "both"),
         Related_Control_2 = str_trim(Related_Control_2, side = "both"),
         Related_Control_3 = str_trim(Related_Control_3, side = "both"),
         Related_Control_4 = str_trim(Related_Control_4, side = "both"),
         Related_Control_5 = str_trim(Related_Control_5, side = "both"),
         Related_Control_6 = str_trim(Related_Control_6, side = "both"),
         Related_Control_7 = str_trim(Related_Control_7, side = "both"),
         Related_Control_8 = str_trim(Related_Control_8, side = "both"),
         Related_Control_9 = str_trim(Related_Control_9, side = "both"),
         Related_Control_10 = str_trim(Related_Control_10, side = "both"),
         Related_Control_11 = str_trim(Related_Control_11, side = "both"),
         Related_Control_12 = str_trim(Related_Control_12, side = "both"),
         Related_Control_13 = str_trim(Related_Control_13, side = "both"),
         Related_Control_14 = str_trim(Related_Control_14, side = "both"),
         Related_Control_15 = str_trim(Related_Control_15, side = "both"),
         Related_Control_16 = str_trim(Related_Control_16, side = "both"),
         Related_Control_17 = str_trim(Related_Control_17, side = "both"),
         Related_Control_18 = str_trim(Related_Control_18, side = "both"),
         Related_Control_19 = str_trim(Related_Control_19, side = "both"),
         Related_Control_20 = str_trim(Related_Control_20, side = "both"),
         Related_Control_21 = str_trim(Related_Control_21, side = "both"),
         Related_Control_22 = str_trim(Related_Control_22, side = "both"),
         Related_Control_23 = str_trim(Related_Control_23, side = "both"),
         Related_Control_24 = str_trim(Related_Control_24, side = "both"),
         Related_Control_25 = str_trim(Related_Control_25, side = "both"),
         Related_Control_26 = str_trim(Related_Control_26, side = "both"),
         Related_Control_27 = str_trim(Related_Control_27, side = "both"),
         Related_Control_28 = str_trim(Related_Control_28, side = "both")) #removing empty spaces in those variable's values. 
```

##Spreading Related Control into different columns and gathering the control enhancement by main controls (removing the control enhancement detail).
**Gephi_Controls2**
```{r warning = FALSE}
Gephi_Controls2 <- Gephi_Controls %>%
  select(-Control_Enhancement, -Combined) %>%
  separate(Related_Controls, paste("Related_Control", 1:28, sep = "_"),
           sep = ",", 
           extra = "warn") %>% #spreading Related Controls into different columns
  gather(AllRelatedControls, Value, 
         Related_Control_1:Related_Control_28, na.rm = TRUE) %>%
  group_by(Main_Control) %>%
  mutate(AllRelatedControls2 = paste("Related_Control", 1:n(), sep = "_")) %>% 
  ungroup() %>%
  select(-AllRelatedControls) %>%
  spread(AllRelatedControls2, Value, convert = TRUE) %>% 
  select(Control_Family, Family_Name, Main_Control, Control_Name, #Low, Medium, High, Impact,
         Related_Control_1, Related_Control_2, Related_Control_3, Related_Control_4, Related_Control_5,
         Related_Control_6, Related_Control_7, Related_Control_8, Related_Control_9, Related_Control_10,
         Related_Control_11, Related_Control_12, Related_Control_13, Related_Control_14, Related_Control_15,
         Related_Control_16, Related_Control_17, Related_Control_18, Related_Control_19, Related_Control_20,
         Related_Control_21, Related_Control_22, Related_Control_23, Related_Control_24, Related_Control_25,
         Related_Control_26, Related_Control_27, Related_Control_28, Related_Control_29, Related_Control_30,
         Related_Control_31, Related_Control_32, Related_Control_33, Related_Control_34, Related_Control_35,
         Related_Control_36, Related_Control_37) %>% #reording the variables in the table 
  mutate(Related_Control_1 = str_trim(Related_Control_1, side = "both"),
         Related_Control_2 = str_trim(Related_Control_2, side = "both"),
         Related_Control_3 = str_trim(Related_Control_3, side = "both"),
         Related_Control_4 = str_trim(Related_Control_4, side = "both"),
         Related_Control_5 = str_trim(Related_Control_5, side = "both"),
         Related_Control_6 = str_trim(Related_Control_6, side = "both"),
         Related_Control_7 = str_trim(Related_Control_7, side = "both"),
         Related_Control_8 = str_trim(Related_Control_8, side = "both"),
         Related_Control_9 = str_trim(Related_Control_9, side = "both"),
         Related_Control_10 = str_trim(Related_Control_10, side = "both"),
         Related_Control_11 = str_trim(Related_Control_11, side = "both"),
         Related_Control_12 = str_trim(Related_Control_12, side = "both"),
         Related_Control_13 = str_trim(Related_Control_13, side = "both"),
         Related_Control_14 = str_trim(Related_Control_14, side = "both"),
         Related_Control_15 = str_trim(Related_Control_15, side = "both"),
         Related_Control_16 = str_trim(Related_Control_16, side = "both"),
         Related_Control_17 = str_trim(Related_Control_17, side = "both"),
         Related_Control_18 = str_trim(Related_Control_18, side = "both"),
         Related_Control_19 = str_trim(Related_Control_19, side = "both"),
         Related_Control_20 = str_trim(Related_Control_20, side = "both"),
         Related_Control_21 = str_trim(Related_Control_21, side = "both"),
         Related_Control_22 = str_trim(Related_Control_22, side = "both"),
         Related_Control_23 = str_trim(Related_Control_23, side = "both"),
         Related_Control_24 = str_trim(Related_Control_24, side = "both"),
         Related_Control_25 = str_trim(Related_Control_25, side = "both"),
         Related_Control_26 = str_trim(Related_Control_26, side = "both"),
         Related_Control_27 = str_trim(Related_Control_27, side = "both"),
         Related_Control_28 = str_trim(Related_Control_28, side = "both"),
         Related_Control_29 = str_trim(Related_Control_29, side = "both"),
         Related_Control_30 = str_trim(Related_Control_30, side = "both"),
         Related_Control_31 = str_trim(Related_Control_31, side = "both"),
         Related_Control_32 = str_trim(Related_Control_32, side = "both"),
         Related_Control_33 = str_trim(Related_Control_33, side = "both"),
         Related_Control_34 = str_trim(Related_Control_34, side = "both"),
         Related_Control_35 = str_trim(Related_Control_35, side = "both"),
         Related_Control_36 = str_trim(Related_Control_36, side = "both"),
         Related_Control_37 = str_trim(Related_Control_37, side = "both")) #removing empty spaces in those variable's values. 
```    

##Similar to Gephi_Controls2 but reformatted to make it easier to manipulate.
**Gephi_Controls4**
```{r}
Gephi_Controls4 <- Gephi_Controls1 %>%
  select (-Combined) %>%
  gather(AllRelatedControls, Value, Related_Control_1:Related_Control_28, na.rm = TRUE) %>%
  group_by(Main_Control) %>%
  mutate(AllRelatedControls2 = paste("Related_Control", 1:n(), sep = "_")) %>%
  rename(Related_Controls = Value) %>%
  select(-AllRelatedControls, -AllRelatedControls2) %>%
  ungroup() %>%
  arrange(Main_Control) 
```

##Removes duplicates if the main control has two of the same related controls
**Gephi_Controls5 & Gephi_Controls6**
```{r}
#This removes 36 duplicates (ex. AU-6 & AU-12, AC-18 & AC-19)
Gephi_Controls5 <- unique(Gephi_Controls4)

#This provideds a new column -- "Weight" -- counts on the duplicates
Gephi_Controls6 <- Gephi_Controls4 %>%
  # (Main_Control, Control_Name, Control_Family, Family_Name, Related_Controls )
  group_by(Control_Family, Family_Name, Main_Control, Control_Name, Related_Controls) %>%
  summarise(n = n()) %>%
  rename("Weight"=n) #%>%
  #arrange(desc(Weight))
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Network Preparation##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Creating Node table
```{r}
#Capturing distinct Main Controls
nodes <- distinct(Controls_mod, Control_Family, Family_Name, Main_Control, Control_Name)

#Adding Label column  
nodes["Label"] = nodes$Main_Control 

#Reordering and renaming columns
nodes <- nodes %>%
  select (Main_Control, Label, Control_Name, Control_Family, Family_Name) %>%
  rename("Id" = Main_Control) 

nodes = nodes[complete.cases(nodes$Id),]

#Write to CSV 
write_csv(nodes, "Nodes.csv") #exporting the Node file into a csv file called Nodes.csv into your working directory you set earlier.
```

##Creating Edge table
```{r}
edges <- Gephi_Controls4 %>%
  group_by(Main_Control, Related_Controls) %>%
  summarise(n = n()) %>%
  rename(Source = Main_Control, Target = Related_Controls, Weight=n) #%>%
  #arrange(desc(Weight))

#Write to CSV
write_csv(edges, "Edges.csv") #exporting the Edge file into a csv file called Edges.csv into your working directory you set earlier.
```

##Load edge and node files if needed.  Only include complete nodes and build graph.
```{r}
#node_file = '/Users/eugenehwang/Documents/GitHub/FedRAMP_800-53_Controls/Gephi/Nodes.csv'
#edge_file = '/Users/eugenehwang/Documents/GitHub/FedRAMP_800-53_Controls/Gephi/Edges.csv'

#nodes = read.csv(node_file, header = T)
#nodes = nodes[complete.cases(nodes$Id),]
#edges = read.csv(edge_file, header = T)
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Network Functions##
##These are the main functions used to create and analyze our network.##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**

##Load Functions
**This function builds the graph with all of the node and edge level attributes that are found in the data provided or derived by the data provided.**
```{r}
build_graph <- function (nodes, edges) {
  g = graph.empty(nrow(nodes), directed = TRUE)
  # covert R factor to character
  V(g)$name = as.character(nodes$Id)
  V(g)$Label = as.character(nodes$Label)
  V(g)$Control_Name = as.character(nodes$Control_Name)
  V(g)$Control_Family = as.character(nodes$Control_Family)
  V(g)$Family_Name = as.character(nodes$Family_Name)
  
  # a edge array: odd index -> source, even index -> target
  edge_list = as.vector(t(cbind(as.character(edges$Source), as.character(edges$Target))))
  g = add_edges(g, edge_list)
  E(g)$weight = edges$Weight 

  return(g)
}
```

##The next functions are essential for calculating the network level statistics.
**This function calculates assortativity, which is a single statistic measuring the degree of connections betweeen similiar nodes.**
```{r}
get_assortativity <- function(g, attr) {
  cat = igraph::get.vertex.attribute(g, attr )
  #!! have to convert vertex values from chartacter to factor
  assortativity = assortativity_nominal(g, as.factor(cat), directed = F)
  return(assortativity);
}
```

**This function is used to calculate average degree, which calculates the average connections per node for each attribute specified.**
```{r}
get_degree <- function(g, attr){
  cat = igraph::get.vertex.attribute(g, attr )
  V(g)$degree = igraph::degree(g)
  V(g)$strength = igraph::strength(g)
  return(g)
}
```

**This function calculates the transitivity, which measures how tightly knit a community is.**
**A high transitivity measure indicates a tightly knit collaborative environment (clique), while a low transitivity measure indicates that neighboring researchers do not collaborate with each other (star).**
```{r}
get_transitivity <- function(g) {
  cc = transitivity(g, type='local', vids=V(g)$name)
  V(g)$cc = cc 
  return(g)
}
```

**This function calculates a confusion matrix which generates percentages associated with frequencies of collaboration across levels of a particular attribute.**
```{r}
# calcuate a confusion table between groups 
get_group_confusion <- function(nodes, edges, attr) {
  from_to = select(edges, Source, Target)
  from_to$Source = as.character(from_to$Source)
  from_to$Target = as.character(from_to$Target)
  nodes$Id = as.character(nodes$Id)
  from_to = left_join(from_to, nodes, by= c('Source' = 'Id'))
  from_to = left_join(from_to, nodes, by= c('Target' = 'Id'))
  x = paste0(attr, '.x')
  y = paste0(attr, '.y')
  #x = paste0('Group', '.x')
  #y = paste0('Group', '.y')
  cols <- c(x, y)
  colNums <- match(cols,colnames(from_to))
  fg_tg = select_(from_to, x, y)
  colnames(fg_tg) = c('node_a', 'node_b')
  Source_Groups = as.factor(fg_tg$node_a);
  Target_Groups = as.factor(fg_tg$node_b);
  tbl = table(Source_Groups, Target_Groups)
  prop_table = prop.table(tbl)
  #since it is undirected graph, convert it into triangular
  p1 = prop_table;
  p2 = t(prop_table);
  p3 = p1 + p2
  p4 = lower.tri.remove(p3)
  diag(p4) = diag(p4) / 2
  prop_table = p4
  return(prop_table)
}
```

####OLDDDDDD
```{r}
# calcuate a confusion table between groups 
get_group_confusion <- function(nodes, edges, attr) {
  from_to = select(edges, Source, Target)
  from_to$Source = as.character(from_to$Source)
  from_to$Target = as.character(from_to$Target)
  nodes$Id = as.character(nodes$Id)
  from_to = left_join(from_to, nodes, by= c('Source' = 'Id'))
  from_to = left_join(from_to, nodes, by= c('Target' = 'Id'))
  #x = paste0(attr, '.x')
  #y = paste0(attr, '.y')
  x = paste0('Family_Name', '.x')
  y = paste0('Family_Name', '.y')
  cols <- c(x, y)
  colNums <- match(cols,colnames(from_to))
  fg_tg = select_(from_to, x, y) 
  #^ This causes an issue due to an older version of dplyr which is not compatible with the current version of RStudio.
  ## It adds the grouping variable as a new column, which causes cascading issues.
  ## One way to resolve the issue is to ungroup, as shown below.
  #fg_tg <- from_to %>% group_by(Source) %>% ungroup() %>% select(x,y)
  colnames(fg_tg) = c('node_a', 'node_b')
  Source_Groups = as.factor(fg_tg$node_a);
  Target_Groups = as.factor(fg_tg$node_b);
  tbl = table(Source_Groups, Target_Groups)
  prop_table = prop.table(tbl)
  #since it is undirected graph, convert it into triangular
  p1 = prop_table;
  p2 = t(prop_table);
  p3 = p1 + p2
  p4 = lower.tri.remove(p3)
  diag(p4) = diag(p4) / 2
  prop_table = p4
  return(prop_table)
}
```

**This function counts the number of cliques with "n" connected nodes in the network. For our analysis, we used this function to count complete triads.**
```{r}
# looping through clique to count group membership in clique 
get_cliques_membership <- function(g, n, attr) {
  cs  = cliques(g, min=n)
  cs_len = sapply(cs, length)
  cs_n = cs[cs_len == n]
  cat = unique(igraph::get.vertex.attribute(g, attr))
  numCli = length(cs_n)
  m = matrix(0, nrow = numCli, ncol = length(cat))
  colnames(m) = cat
  #looping throught cliques to count membership by groups
  for (i in 1:numCli) {
    c = cs_n[[i]]
    a = vertex_attr(g,attr, c)
    for (ct in cat) {
      m[i,ct] = sum(a==ct)
    }
  }
  return(m)
}
```

**This function takes the confusion matrix and adjusts the percentages to reflect the percentages to be a proportion of the particular level of an attribute rather than reflecting the overall distribution.**
```{r}
get_confusion_within_group <- function(prop_table) {
  conf_mtx <- prop_table
  conf_mtx[lower.tri(conf_mtx)]<-t(conf_mtx)[lower.tri(conf_mtx)]
  conf_mtx <- data.frame(conf_mtx) %>% dplyr::mutate(Source_Groups = as.character(Source_Groups), 
                                                     Target_Groups = as.character(Target_Groups))
  lvl <- unique(conf_mtx$Source_Groups)
  conf_mtx[,"percent_within"] = NA
  for (i in 1:nrow(conf_mtx)){
    for (j in 1:length(lvl)){
      if (conf_mtx[i,"Source_Groups"] == lvl[j]){
        sum_relevant_rows <- conf_mtx %>% dplyr::filter(Source_Groups == lvl[j])
        sum_relevant_rows <- sum(sum_relevant_rows$Freq)
        conf_mtx[i,"percent_within"] = as.numeric(conf_mtx[i,"Freq"])/sum_relevant_rows
      }
      else {return}
    }
  }
  return(conf_mtx)
}
```

**This function takes the output of the previous function to calculate the within and outside group collaboration for levels of a particular attribute.**
```{r}
get_in_out_tbl <- function(conf_mtx){
  sum_tbl <- conf_mtx %>% dplyr::group_by(Source_Groups) %>% 
    dplyr::summarise(dist = sum(Freq)) %>%
    select(Source_Groups,dist) %>% 
    filter(is.na(dist)==FALSE) %>% 
    arrange(desc(dist))
  in_out_pct <- conf_mtx %>% 
    dplyr::mutate(match = ifelse(Source_Groups == Target_Groups,"within group","outside group"), 
                  percent_within = ifelse(is.na(percent_within)==TRUE, 0, percent_within)) %>% 
    dplyr::group_by(Source_Groups, match) %>% 
    dplyr::summarise(in_out_pct = sum(percent_within))
  return(in_out_pct)
}
```

**This functions use the utility functions listed above to get the overall network statistics.**
```{r}
analyze_graph <- function(g, nodes, edges, attr) {
  #attr: Family Name
  stats = list()
  print(attr)
  
  # 1.Assortativity
  assortativity = get_assortativity(g, attr)
  stats$assortativity = assortativity
  
  # 2. Average degree, Transtivity, and Degee distributions
  g = get_degree(g, attr)
  g = get_transitivity(g)
  var = vertex_attr(g, attr)
  lvls =  unique(var)
  lvl_len = length(lvls)
  dgs = list()
  trs = list()
  strs = list()
  dg_dist = list()
  for (i in 1:lvl_len) {
    lvl = lvls[i]
    lvl_nodes = V(g)[var == lvl]
    dgs[[lvl]] = mean(lvl_nodes$degree,  na.rm = TRUE)
    trs[[lvl]] = mean(lvl_nodes$cc,  na.rm = TRUE)
    strs[[lvl]] = mean(lvl_nodes$strength,  na.rm = TRUE)
    dg = degree.distribution(g, v=lvl_nodes)
    dg_dist[[lvl]] = dg
  }
  dgs[['all_nodes']] =   mean(V(g)$degree, na.rm = TRUE)
  strs[['all_nodes']] =   mean(V(g)$strength, na.rm = TRUE)
  all_dg = degree.distribution(g)
  dg_dist[['all_nodes']] = all_dg
  
  stats$degree = dgs
  stats$strength = strs
  stats$transitivity = trs
  stats$degree_dist =  dg_dist

  # 3. Confusion matrix dyad level
  prop_table = get_group_confusion(nodes, edges, attr)
  stats$prop_table = prop_table

  # 3a. Within group vs Outside group %
  in_out_table = get_in_out_tbl(get_confusion_within_group(prop_table))
  stats$in_out_table = in_out_table
  
  ## Calcuate graph level statistics
  ## The ratio of the number of edges and the number of possible edges
  stats$density = edge_density(g, loops=FALSE)

  ## Count group membership in complete triad graph
  print(paste(rep('#', 30),collapse = ''))
  n = 3 
  m = get_cliques_membership(g, n, attr)

  triad_counts = list()
  for (i in 1:lvl_len) {
    lvl = lvls[i]
    lvl_nodes = V(g)[var == lvl]
    triad_count = sum(m[, lvl] == 3)
    triad_counts[[lvl]] = triad_count
  }
  stats$triads_counts = triad_counts
  return(stats)
}

get_stats <- function(g, attr) {
  all_years_stats = analyze_graph(g, nodes, edges, attr)
  stats = list()
  stats[['all_years_stats']] = all_years_stats
  return(stats)
}
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Plotting Functions##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
**This function plots the confusion matrix as a heat map.**
```{r}
plot_block_heatmap <- function(conf) {
  conf.l = melt(conf)
  ggplot(conf.l, aes(Source_Groups, Target_Groups)) + geom_tile(aes(fill = value),colour = "white")  +  
  scale_fill_gradient(low = "white", high = "steelblue") +
 theme(axis.text.x = element_text(angle = 90, hjust = 1))
}
```

**This function plots the within and outside group percentages by level of attribute.**
```{r}
plot_in_out <- function(stats, attr_name){
  plot.data <- stats$all_years_stats$in_out_table %>% 
    arrange(Source_Groups, desc(match))
  plot.data$Source_Groups <- as.factor(plot.data$Source_Groups)
  ggplot(data=plot.data, aes(x=Source_Groups, y=in_out_pct, fill=match)) +
    geom_bar(stat='identity') + coord_flip() +
    scale_fill_manual(values=c("slategray2", "navyblue")) +
    xlab(attr_name) + ylab("Percentage of Control Family") + 
    ggtitle("Percentage of Collaboration Within and Outside of Control Family") 
}
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Printing Functions##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
**This function prints the statistics.**
```{r}
print_stat <- function(all_years_stats) {
  
  #Print Assortativity
  print(paste(c(rep('#', 15), 'assortativity', rep('#', 15)),collapse = ''))
  print(paste0('assortativity: ', as.character(all_years_stats$assortativity)))
  cat('\n')
  cat('\n')
  
  #Print Degree
  print(paste(c(rep('#', 15), 'Degree', rep('#', 15)),collapse = ''))
  dgs = all_years_stats[['degree']]
  dns = names(dgs)
  for (d in dns) {
    print(paste0('Average ', d,  ' Degree: ', sprintf("%.6f",dgs[[d]] )))
  }
  cat('\n')
  cat('\n')
  
  #Print Confusion table
  print(paste(c(rep('#', 15), 'Confusion Table', rep('#', 15)),collapse = ''))
  print(all_years_stats$prop_table)
  cat('\n')
  cat('\n')
  
  #Print Transitivity
  print(paste(c(rep('#', 15), 'Transitivity', rep('#', 15)),collapse = ''))
  print('The below statistics ignore nodes without edges')
  trs = all_years_stats[['transitivity']]
  tns = names(trs)
  for (t in tns) {
    print(paste0('Average ', t,  ' Transitivity: ', sprintf("%.6f",trs[[t]] )))
  }
  cat('\n')
  cat('\n')
  
  #print Triad count
  print(paste(c(rep('#', 15), 'Complete Triads', rep('#', 15)),collapse = ''))
  t_c = all_years_stats[['triads_counts']]
  tns = names(t_c)
  for (t in tns) {
    print(paste0('The number of  ', t,  ' Complete Triads: ', sprintf("%.6f",t_c[[t]] )))
  }
  cat('\n')
  cat('\n')
}
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Metric Analysis by Family Name##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
**Build igraph table**
```{r}
g <- build_graph(nodes, edges)  

#View Edge and Vertices table
E(g)[[]]     # The edges of the "net" object
V(g)[[]]     # The vertices of the "net" object
plot(g)
```

**Gather stats by Family Name**
```{r warning = FALSE}
q1_stats = get_stats(g, attr='Family_Name')
```

**Print and plot graphs**
```{r, echo=FALSE}
print('Q1: Do control families relate with each other more of then than with other control families?')
q1_all_years_stats = q1_stats[['all_years_stats']] 
print_stat(q1_all_years_stats)
plot_block_heatmap(q1_all_years_stats$prop_table)
plot_in_out(q1_stats,"Control Families")
```



