---
Title: "FedRAMP High Baseline Controls Analysis"
---
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Install and load the following packages##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
```{r, results='hide'}
#install.packages("readxl")
#install.packages("readr")
#install.packages("tidyverse")
```

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(readr)
library(tidyverse)
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Data Cleaning##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##800-53 subcontrol relations
```{r}
#File path
Controls <- read_excel("/Users/eugenehwang/Documents/GitHub/FedRAMP_800-53_Controls/800-53 subcontrol relations.xlsx")

#Set working directory path
setwd("/Users/eugenehwang/Documents/GitHub/FedRAMP_800-53_Controls/Gephi")

#Get working directory path
getwd()

#Selecting only the columns needed and renaming columns with underscore **
Controls_mod <- Controls

names(Controls_mod) <- c("Control_Family","Family_Name","Control_Name", "Main_Control","Control_Enhancement_Name", "Control_Enhancement","Combined","Related_Controls","Low","Low_1","Tailoring_Action","Medium","Medium_1","High","High_1","Priority","Impact")

#Only looking at High Impact Controls
Gephi_Controls <- Controls_mod %>%
  filter(High == "Y") %>% #filtering to High Baseline
  select(Control_Family, Family_Name, Main_Control, Control_Name, Control_Enhancement, Combined, Related_Controls)
         #,Low, Medium, High, Impact, Tailoring_Action) 
```

##Spreading Related Controls into different columns.
**Gephi_Controls1**
```{r warning = FALSE}
Gephi_Controls1 <- Gephi_Controls %>%
  select(-Control_Enhancement) %>%
  separate(Related_Controls, paste("Related_Control", 1:28, sep = "_"),
           sep = ",", 
           extra = "warn") %>% #spreading Related Controls into different columns 
  mutate(Related_Control_1 = str_trim(Related_Control_1, side = "both"),
         Related_Control_2 = str_trim(Related_Control_2, side = "both"),
         Related_Control_3 = str_trim(Related_Control_3, side = "both"),
         Related_Control_4 = str_trim(Related_Control_4, side = "both"),
         Related_Control_5 = str_trim(Related_Control_5, side = "both"),
         Related_Control_6 = str_trim(Related_Control_6, side = "both"),
         Related_Control_7 = str_trim(Related_Control_7, side = "both"),
         Related_Control_8 = str_trim(Related_Control_8, side = "both"),
         Related_Control_9 = str_trim(Related_Control_9, side = "both"),
         Related_Control_10 = str_trim(Related_Control_10, side = "both"),
         Related_Control_11 = str_trim(Related_Control_11, side = "both"),
         Related_Control_12 = str_trim(Related_Control_12, side = "both"),
         Related_Control_13 = str_trim(Related_Control_13, side = "both"),
         Related_Control_14 = str_trim(Related_Control_14, side = "both"),
         Related_Control_15 = str_trim(Related_Control_15, side = "both"),
         Related_Control_16 = str_trim(Related_Control_16, side = "both"),
         Related_Control_17 = str_trim(Related_Control_17, side = "both"),
         Related_Control_18 = str_trim(Related_Control_18, side = "both"),
         Related_Control_19 = str_trim(Related_Control_19, side = "both"),
         Related_Control_20 = str_trim(Related_Control_20, side = "both"),
         Related_Control_21 = str_trim(Related_Control_21, side = "both"),
         Related_Control_22 = str_trim(Related_Control_22, side = "both"),
         Related_Control_23 = str_trim(Related_Control_23, side = "both"),
         Related_Control_24 = str_trim(Related_Control_24, side = "both"),
         Related_Control_25 = str_trim(Related_Control_25, side = "both"),
         Related_Control_26 = str_trim(Related_Control_26, side = "both"),
         Related_Control_27 = str_trim(Related_Control_27, side = "both"),
         Related_Control_28 = str_trim(Related_Control_28, side = "both")) #removing empty spaces in those variable's values. 
```

##Spreading Related Control into different columns and gathering the control enhancement by main controls (removing the control enhancement detail).
**Gephi_Controls2**
```{r warning = FALSE}
Gephi_Controls2 <- Gephi_Controls %>%
  select(-Control_Enhancement, -Combined) %>%
  separate(Related_Controls, paste("Related_Control", 1:28, sep = "_"),
           sep = ",", 
           extra = "warn") %>% #spreading Related Controls into different columns
  gather(AllRelatedControls, Value, 
         Related_Control_1:Related_Control_28, na.rm = TRUE) %>%
  group_by(Main_Control) %>%
  mutate(AllRelatedControls2 = paste("Related_Control", 1:n(), sep = "_")) %>% 
  ungroup() %>%
  select(-AllRelatedControls) %>%
  spread(AllRelatedControls2, Value, convert = TRUE) %>% 
  select(Control_Family, Family_Name, Main_Control, Control_Name, #Low, Medium, High, Impact,
         Related_Control_1, Related_Control_2, Related_Control_3, Related_Control_4, Related_Control_5,
         Related_Control_6, Related_Control_7, Related_Control_8, Related_Control_9, Related_Control_10,
         Related_Control_11, Related_Control_12, Related_Control_13, Related_Control_14, Related_Control_15,
         Related_Control_16, Related_Control_17, Related_Control_18, Related_Control_19, Related_Control_20,
         Related_Control_21, Related_Control_22, Related_Control_23, Related_Control_24, Related_Control_25,
         Related_Control_26, Related_Control_27, Related_Control_28, Related_Control_29, Related_Control_30,
         Related_Control_31, Related_Control_32, Related_Control_33, Related_Control_34, Related_Control_35,
         Related_Control_36, Related_Control_37) %>% #reording the variables in the table 
  mutate(Related_Control_1 = str_trim(Related_Control_1, side = "both"),
         Related_Control_2 = str_trim(Related_Control_2, side = "both"),
         Related_Control_3 = str_trim(Related_Control_3, side = "both"),
         Related_Control_4 = str_trim(Related_Control_4, side = "both"),
         Related_Control_5 = str_trim(Related_Control_5, side = "both"),
         Related_Control_6 = str_trim(Related_Control_6, side = "both"),
         Related_Control_7 = str_trim(Related_Control_7, side = "both"),
         Related_Control_8 = str_trim(Related_Control_8, side = "both"),
         Related_Control_9 = str_trim(Related_Control_9, side = "both"),
         Related_Control_10 = str_trim(Related_Control_10, side = "both"),
         Related_Control_11 = str_trim(Related_Control_11, side = "both"),
         Related_Control_12 = str_trim(Related_Control_12, side = "both"),
         Related_Control_13 = str_trim(Related_Control_13, side = "both"),
         Related_Control_14 = str_trim(Related_Control_14, side = "both"),
         Related_Control_15 = str_trim(Related_Control_15, side = "both"),
         Related_Control_16 = str_trim(Related_Control_16, side = "both"),
         Related_Control_17 = str_trim(Related_Control_17, side = "both"),
         Related_Control_18 = str_trim(Related_Control_18, side = "both"),
         Related_Control_19 = str_trim(Related_Control_19, side = "both"),
         Related_Control_20 = str_trim(Related_Control_20, side = "both"),
         Related_Control_21 = str_trim(Related_Control_21, side = "both"),
         Related_Control_22 = str_trim(Related_Control_22, side = "both"),
         Related_Control_23 = str_trim(Related_Control_23, side = "both"),
         Related_Control_24 = str_trim(Related_Control_24, side = "both"),
         Related_Control_25 = str_trim(Related_Control_25, side = "both"),
         Related_Control_26 = str_trim(Related_Control_26, side = "both"),
         Related_Control_27 = str_trim(Related_Control_27, side = "both"),
         Related_Control_28 = str_trim(Related_Control_28, side = "both"),
         Related_Control_29 = str_trim(Related_Control_29, side = "both"),
         Related_Control_30 = str_trim(Related_Control_30, side = "both"),
         Related_Control_31 = str_trim(Related_Control_31, side = "both"),
         Related_Control_32 = str_trim(Related_Control_32, side = "both"),
         Related_Control_33 = str_trim(Related_Control_33, side = "both"),
         Related_Control_34 = str_trim(Related_Control_34, side = "both"),
         Related_Control_35 = str_trim(Related_Control_35, side = "both"),
         Related_Control_36 = str_trim(Related_Control_36, side = "both"),
         Related_Control_37 = str_trim(Related_Control_37, side = "both")) #removing empty spaces in those variable's values. 
```    

##Similar to Gephi_Controls2 but reformatted to make it easier to manipulate.
**Gephi_Controls4**
```{r}
Gephi_Controls4 <- Gephi_Controls1 %>%
  select (-Combined) %>%
  gather(AllRelatedControls, Value, Related_Control_1:Related_Control_28, na.rm = TRUE) %>%
  group_by(Main_Control) %>%
  mutate(AllRelatedControls2 = paste("Related_Control", 1:n(), sep = "_")) %>%
  rename(Related_Controls = Value) %>%
  select(-AllRelatedControls, -AllRelatedControls2) %>%
  ungroup() %>%
  arrange(Main_Control) 
```

##Removes duplicates if the main control has two of the same related controls
**Gephi_Controls5 & Gephi_Controls6**
```{r}
#This removes 36 duplicates (ex. AU-6 & AU-12, AC-18 & AC-19)
Gephi_Controls5 <- unique(Gephi_Controls4)

#This provideds a new column -- "Weight" -- counts on the duplicates
Gephi_Controls6 <- Gephi_Controls4 %>%
  # (Main_Control, Control_Name, Control_Family, Family_Name, Related_Controls )
  group_by(Control_Family, Family_Name, Main_Control, Control_Name, Related_Controls) %>%
  summarise(n = n()) %>%
  rename("Weight"=n) #%>%
  #arrange(desc(Weight))
```

**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Network Preparation##
**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**~**
##Creating Node table
```{r}
#Capturing distinct Main Controls
nodes <- distinct(Controls_mod, Control_Family, Family_Name, Main_Control, Control_Name)

#Adding Label column  
nodes["Label"] = nodes$Main_Control 

#Reordering and renaming columns
nodes <- nodes %>%
  select (Main_Control, Label, Control_Name, Control_Family, Family_Name) %>%
  rename("Id" = Main_Control) 

nodes = nodes[complete.cases(nodes$Id),]

#Write to CSV 
write_csv(nodes, "Nodes.csv") #exporting the Node file into a csv file called Nodes.csv into your working directory you set earlier.
```

##Creating Edge table
```{r}
edges <- Gephi_Controls4 %>%
  group_by(Main_Control, Related_Controls) %>%
  summarise(n = n()) %>%
  rename(Source = Main_Control, Target = Related_Controls, Weight=n) #%>%
  #arrange(desc(Weight))

#Write to CSV
write_csv(edges, "Edges.csv") #exporting the Edge file into a csv file called Edges.csv into your working directory you set earlier.


#Duplicate Combinations Testing

edges_duplicates <- subset(edges, Source=="AU-6" & Target == "AU-12" | Source == "AU-12" & Target == "AU-6" | Source=="AC-14" & Target == "CP-2" | Source == "CP-2" & Target == "AC-14")

edges_duplicates["Combined"] <- paste(c(1:2), sep = "")


```






























